Potential of I/O-Aware Workflows in Climate and Weather

### 2020-02-20 paper.tex
Stronger abstract

\begin{abstract}
The efficient, convenient, and robust execution of data-driven workflows and enhanced data management are key for productivity in scientific computing.
Traditionally, in HPC, the concerns of storage and computing are separated and optimised independently from each other and the needs of the end-to-end user.

As climate and weather workflows become increasingly complex and blended beyond data centres while, at the same time, storage hierarchies become deeper, the community investigates ways to reorganise storage access to utilise such systems fully.

The key contributions of this paper are:
1) we sketch the vision of an integrated data-driven approach and discuss the challenges and implications of this strategy, and 2) we illustrate architecture and roadmap that allows the seamless integration into current climate and weather workflows.
The tools employed here to achieve an extended workflow are Cylc, XIOS, DDN IME, and ESDM.

We believe workflows composed of data, computing, and communication-intensive tasks should drive the interfaces and hardware configurations to best support the programming models.
The changes proposed here increase the opportunity of implementations for smarter scheduling of computing and storage in heterogeneous storage systems.

>>>>

\begin{abstract}
The efficient, convenient, and robust execution of data-driven workflows and enhanced data management are key for productivity in scientific computing. 
In HPC, the concerns of storage and computing are traditionally separated and optimised independently from each other and the needs of the end-to-end user, but in complex workflows this is becoming problematic. These problems are particularly acute in climate and weather workflows, which as well as become increasingly complex and exploiting deep storage hierarchies, can involve multiple data centres.

The key contributions of this paper are:
1) A sketch of a vision for an integrated data-driven approach, with a discussion of the associated  challenges and implications, and 2) An architecture and roadmap consistent with that vision that would allow seamless integration into current climate and weather workflows as it utilises versions of mostly existing tools (Cylc, XIOS, DDN IME, and ESDM).

This vision is built on the belief that workflows composed of data, computing, and communication-intensive tasks should drive  interfaces and hardware configurations to best support the programming models. 
When delivered, the work proposed here will increase the opportunity for smarter scheduling of computing and storage in heterogeneous storage systems.
